---
title: Plotting a Volcano
author: Hywel Stoakes
date: '2019-01-29'
slug: plotting-a-volcano
summary: "Using R code in markdown to plot a volcano (not just any volcano)."
authors: [hywel]
categories:
  - Academia
tags:
  - R
  - home
header:
  caption: ''
  image: ''
  preview: yes
---

This post is a test of the capabilities of the Blogdown R package and the Hugo Academia Theme. I thought that I would play with a bit of **R** code while I have the opportunity. Last year I could see this volcano from my window of my house so it was my Maunga then. I feel that it still is, spiritually. Among other things, it kept me fit running up to the [*tihi*](https://maoridictionary.co.nz/search?idiom=&phrase=&proverb=&loan=&histLoanWords=&keywords=tihi). Here is a small snippet from my [*Pepeha*](https://maoridictionary.co.nz/search?idiom=&phrase=&proverb=&loan=&histLoanWords=&keywords=pepeha) (2):

> Kei Maunga Whau ahau e noho ana

The plot below uses geospatial data, included in the R base package. I think this neatly shows the New Zealand roots of the *R* software package. I feel a real sense of place thinking about the well-trodden path from the mountain to the University of Auckland, city campus.

The code below comes from: [Fifty ways to draw a volcano using package plot3D](https://cran.r-project.org/web/packages/plot3D/vignettes/volcano.pdf) by Karline Soetaert

```{r setup}
# Preamble
library(plot3D)
# Reduce the resolution
 Volcano <- volcano[seq(1, nrow(volcano), by = 3),
                     seq(1, ncol(volcano), by = 3)]


```

```{r Plot}
image2D(Volcano, lighting = TRUE, rasterImage = TRUE,
     contour = list(col = "white", labcex = 0.8, lwd = 3, alpha = 0.5))
```

Unfortunately my chance to map and describe Maunga Whau has been put on hold by COVID. Maunga Whau is a much loved Auckland landmark and I know I'm not the only one fascinated by the [Maunga](https://maoridictionary.co.nz/search?idiom=&phrase=&proverb=&loan=&histLoanWords=&keywords=maunga) of Te Ika-a-MÄui, Aotearoa.

