---
title: A Major Rebuild
author: Hywel Stoakes
date: '2020-11-10'
slug: a-major-rebuild
categories:
  - Admin
tags:
  - Phonetics
  - R
  - home
subtitle: 'A site refresh'
summary: 'I needed to modernize the version of Hugo and Blogdown I am using.'
authors: [admin]
lastmod: '2020-11-10T17:03:31+11:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

I realised a few months back that my personal website had stopped updating and that I needed to put in some work to get it back up and running. In addition, my domain name had expired and I had no idea how to migrate without some serious headaches. I revived the domain name, but found the content was seriously out of date. I have since moved institution and country and needed to either pull the site or update. 

Consequently, I needed a plan to either migrate or recreate the posts. Most of the previous site was just a place to put some of my papers rather than a blogging platform. I have never been a very diligent blogger and have often left site languishing. [See this old github site](https://hywel.github.io) which is now broken completely apart from the twitter feed.

I really didn't want to move away from using Blogdown to update the site because I am so heavily invested in the **R** ecosystem and most of my analysis work uses it and Rmarkdown. I thought I would document a couple of the steps I took in the rebuild. In essence I just backed up and then deleted the site and re-downloaded the Hugo Academic template, adding in old posts and content very carefully. Most of the installation information below come directly from [the blogdown book](https://bookdown.org/yihui/blogdown/).

```{r, eval=FALSE}
## Install from CRAN
install.packages('blogdown') 
## Or, install from GitHub
if (!requireNamespace("devtools")) install.packages('devtools')
devtools::install_github('rstudio/blogdown')
```

I then updated Hugo from within Rstudio
```{r, eval=FALSE}
blogdown::update_hugo()
```

This is the version of Hugo that I am running
```{r}
blogdown::hugo_version()
```

### blogdown version:

Yihui Xie (2020). blogdown: Create Blogs and Websites with R
  Markdown. R package version 0.21.


