---
title: A Major Rebuild
author: Hywel Stoakes
date: '2020-11-10'
slug: a-major-rebuild
categories:
  - Admin
tags:
  - Phonetics
  - R
  - home
subtitle: 'A site refresh'
summary: 'I needed to modernize the version of Hugo and Blogdown I am using.'
authors: [hywel]
lastmod: '2020-11-10T17:03:31+11:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

I realised a few months back that my personal website had stopped updating and that I needed to put in some work to get it back up and running. In addition, my domain name had expired and I had no idea how to migrate without some serious headaches. I revived the domain name, but realised the version of the site that was served was seriously out of date. It was an entirely static site and the pipeline I was using to update the content had stopped updating. In the interim I have moved institution and country and I came to the conclusion that I needed to either pull the site or update it with a more modern architecture.

I needed a plan to either migrate to a new site and recreate the posts or patch together what I already had. Most of my previous site was used as a place to store some of my papers rather than used as a blogging platform. I have never been a very diligent blogger and have often left sites languishing preferring to create new sites rather than updating old content. [See this old github site](https://hywel.github.io) which is now broken completely apart from the twitter feed.

I really didn't want to move away from using Blogdown to update the site because I am so heavily invested in the **R** ecosystem and most of my analysis work uses it and Rmarkdown. I thought I would document a couple of the steps I took in the rebuild. In essence I just backed up and then deleted the site and re-downloaded the Hugo Academic template, adding in old posts and content very carefully. Most of the installation information below come directly from [the blogdown book](https://bookdown.org/yihui/blogdown/).

```{r, eval=FALSE}
## Install from CRAN
install.packages('blogdown') 
## Or, install from GitHub
if (!requireNamespace("devtools")) install.packages('devtools')
devtools::install_github('rstudio/blogdown')
```

I then updated Hugo from within Rstudio

```{r, eval=FALSE}
blogdown::update_hugo()
```

This is the version of Hugo that I am running:

```{r}
blogdown::hugo_version()
```

Below is the theme that I ended up using, which is an update of the original theme. And this is the command I used to install it.

```{r, eval=FALSE}
blogdown::new_site(theme = 'wowchemy/starter-academic')
```

There is a fair bit of customisation that needs to be done in the `config/_default` folder and the `content/home` folder. This is where you can choose to remove pages and content. The documentation is fairly easy to follow ([here](https://wowchemy.com/docs/)).

I use [Netlify](https://www.netlify.com) to serve the site as recommended by Yihui Xie and Blogdown. This seems to be fairly stable and I can get Netlify to build the site using Hugo in only a couple of seconds.

### blogdown version:

Yihui Xie (2020). blogdown: Create Blogs and Websites with R Markdown. R package version 0.21.
